Title\tnoteref{label1}

### 2015-05-09 papers/webservice-coalition-learning-elsevier-template/elsarticle-template-num.tex
rabeb comments-2

\journal{Decision Support Systems}

@@

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

@@

\begin{abstract}
Web services are loosely-coupled business applications willing to cooperate in distributed settings within different groups called communities. Communities aim to provide web services with better visibility, efficiency, market share and total payoff. A number of mechanisms and models have been recently proposed to aggregate web
services and make them cooperate within their communities. However, existing community models mostly focus on short term goals. Moreover, these models generally suffer from high computational complexity, which makes decision making about community formation in real-time extremely hard, time consuming, and even impossible in some complex cases. In this paper, we propose a strategic distributed decision making mechanism called DDM that regulates web service agents' decision making process, which is about deciding with whom to cooperate. This model first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. The decision making mechanism implements a decision tree of possible viable strategies and their long-term expected utility gain.
%Utilizing the training model, the decision making mechanism implements a decision tree with an estimation of long-term utility gain for the web services. Communities can used the trained model and instantly choose best-response strategies considering their long-term gain. 
Our model helps 1) communities of web services efficiently find the appropriate web service to invite as new member; and 2) single web services find best communities to join. After being trained, web services get to compute expectations as utilities they would gain if cooperating with communities of different characteristics. In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated initiated by a web service. In general, DDM equips web services with efficient methods of foreseeing how their choices of actions would impact their short-term and long-term goals, therefore opting for better decisions. We performed experiments using real data from 142 users on 4,532 web services on 64 different time slots. The experimental results, show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.
\end{abstract}

\begin{keyword}
Web services\sep Community of services\sep Distributed Decision Making
%% keywords here, in the form: keyword \sep keyword

@@

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

@@

\IEEEPARstart{O}{ver} the past years, online services have become an important part of many scalable business applications. The increasing reliance on online service providers has significantly influenced the way web services are engineered. Therefore, given the dynamic and unpredictable nature of the Internet, delivering high quality services is still a critical and challenging issue. One practical solution towards delivering high quality services is utilizing intelligent decision making agents. These agents aim at maximizing their gain by exploring the best ways to provide services that satisfy end users\cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, journals/tsc/ZhengZYB13, Demirkan2013412}. However, agent-based web services are functionally limited in the sense that they cannot handle a large number of requests at the same time without compromising the quality of service provided. Recent developments have attempted to shift web services from passive models, consisting of individual components, to models made up of autonomous and group-based components that share common goals. In group-based models, interaction, composition, and cooperation are the key challenges \cite{ICWS2011-1, SCC2011-1, journals/mags/BaldoniBM10, journals/jcss/CasadoYT13} that directly impact the group's overall performance in achieving common goals. To that end, we see the emergence of web service \emph{communities}, which consist of services with similar functionalities but distinct nonfunctional properties \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic, 10.1109/ARES.2008.7}. A \emph{community} of web services runs continuous performance assessment functions that regulate web services' interactions and manage their composition and cooperation.

@@

%- We want to give full distributed control to web services as autonomous agents and distribute the task of community management among all web services and let them decide how to maximize their efficiency and join and create communities.
%- Let agents train and learn long term expectations of each action and group they can join with
%- Web services cannot find the optimal solution in big space problem of many web services
%- Add rationalism and less vague decisions

%Web services provide a set of stateless software functions accessible at a network address over the web. 
%Online autonomous agent-based services are software systems providing a standard way of interoperability among different applications.

% - The recent developments are shifting web services from passive and individual components to autonomous and group-based components where interactiion, composition, and cooperation are the key challenges.

%- High demand on online services has created a massive business competition. For example, nowadays users are provided with multiple choices of web services offering local places information such as coffees, venues, and shops nearby a geographic position. It is hard for new web services to find their customers and be visible for end users amongst hundreds or thousands of other available services, even if they provide a high quality of service. Hence, the concept of communities of web services provides them with the chance of joining a platform with an established market share and reputation. However, it is crucial for a community manager to consider many factors when inviting or accepting new members. For example,  this may hurt the community stability.

%- The high competition within the services industry requires applications to use reliable and high quality online service providers. If the user were to check a web site or run an application on her mobile device upon having downtime, or having high response delay or encountering any non-satisfying quality metric, she will instantly remove the application, which is a huge business concern for application providers. For example, if a user installs a ticketing application on her mobile device and the application is not using high quality service providers, the user would instantly uninstall the application, which has an extremely negative impact on the visibility of the application.

%- Most applications cannot independently satisfy users requests and should rely on different online services. The high competition within the services industry requires applications to use reliable and high quality online service providers.

%Today web services are

%- softwares rely on third party online service providers 
%- quality of services determines the success of the business 
%- services want to maximise thier utility by cooperating with best possible communities
%- services need to get visible and join market

% Computer Society journal papers do something a tad strange with the very
% first section heading (almost always called "Introduction"). They place it
% ABOVE the main text! IEEEtran.cls currently does not do this for you.
% However, You can achieve this effect by making LaTeX jump through some
% hoops via something like:
%
%\ifCLASSOPTIONcompsoc
%  \noindent\raisebox{2\baselineskip}[0pt][0pt]%
%  {\parbox{\columnwidth}{\section{Introduction}\label{sec:introduction}%
%  \global\everypar=\everypar}}%
%  \vspace{-1\baselineskip}\vspace{-\parskip}\par
%\else
%  \section{Introduction}\label{sec:introduction}\par
%\fi
%
% Admittedly, this is a hack and may well be fragile, but seems to do the
% trick for me. Note the need to keep any \label that may be used right
% after \section in the above as the hack puts \section within a raised box.

% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps (small caps for compsoc).
%
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
%
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
%
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
%
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
%\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
%for IEEE Computer Society journal papers produced under \LaTeX\ using
%IEEEtran.cls version 1.7 and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
%I wish you the best of success.

%\hfill mds

%\hfill January 11, 2007

@@

\begin{table*}[ht]
\caption{An example of $gain$ matrix for 3 different communities and their combinations} % title of Table
\centering % used for centering table
\scriptsize
{\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|c c c c c c} % centered columns (4 columns)
\hline\hline %inserts double horizontal lines
 & \textless348\textgreater & \textless1934\textgreater & \textless2117\textgreater & \textless348, 1934\textgreater & \textless1934, 2117\textgreater & \textless348, 1934, 2117\textgreater \\ [0.5ex] % inserts table
%heading
\hline % inserts single horizontal line
\textless348\textgreater & - & 0.282708 & 1.027081 & 0.282708 & 18.027081 & 18.027081 \\
\textless1934\textgreater & -2.637483 & - & 6.969072 & -2.637483 & 5.509583 & 4.387725 \\
\textless2117\textgreater & 5.027081 & 2.969072 & - & 5.509583 & 2.969072 & 5.509583 \\
\textless348, 1934\textgreater & 0.0 & 0.0 & -3.851432 & - & -3.851432 & -3.851432 \\
\textless1934, 2117\textgreater & 2.969072 & 0.0 & 0.0 & 2.969072 & - & 2.969072 \\
\textless348, 1934, 2117\textgreater & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & - \\ [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
}
\label{table:nonlin} % is used to refer this table in the text
\end{table*}

@@

%\subsection{Subsection Heading Here}
%Subsection text here.

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

%\subsubsection{Subsubsection Heading Here}
%Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection %text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.
%Subsubsection text here.Subsubsection text here.Subsubsection text here.

%Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection %text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex,
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE CS typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.
% However, the Computer Society has been known to put floats at the bottom.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE CS papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals use top floats exclusively.
% However, Computer Society journals sometimes do use bottom floats - bear
% this in mind when choosing appropriate optional arguments for the
% figure/table environments.
% Note that, LaTeX2e, unlike IEEE journals, places footnotes above bottom
% floats. This can be corrected via the \fnbelowfloat command of the
% stfloats package.

@@

%\bibitem{}

>>>>

\journal{Nuclear Physics B}

@@

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
\title{Title\tnoteref{label1}}
\tnotetext[label1]{}
\author{Name\corref{cor1}\fnref{label2}}
\ead{email address}
%%\ead[url]{home page}
%%\fntext[label2]{}
%%\cortext[cor1]{}
%%\address{Address\fnref{label3}}
%%\fntext[label3]{}

@@

\begin{abstract}
Web services are loosely-coupled business applications willing to cooperate in distributed settings within different groups called communities. Communities aim to provide web services with better visibility, efficiency, market share and total payoff. A number of mechanisms and models have been recently proposed to aggregate web
services and make them cooperate within their communities. However, existing community models mostly focus on short term goals. Moreover, these models generally suffer from high computational complexity, which makes decision making about community formation in real-time extremely hard, time consuming, and even impossible in some complex cases. In this paper, we propose a strategic distributed decision making mechanism called DDM that regulates web service agents' decision making process, which is about deciding with whom to cooperate. This model first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. The decision making mechanism implements a decision tree of possible viable strategies and their long-term expected utility gain.
%Utilizing the training model, the decision making mechanism implements a decision tree with an estimation of long-term utility gain for the web services. Communities can used the trained model and instantly choose best-response strategies considering their long-term gain. 
Our model helps 1) communities of web services efficiently find the appropriate web service to invite as new member; and 2) single web services find best communities to join. After being trained, web services get to compute expectations as utilities they would gain if cooperating with communities of different characteristics. In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated initiated by a web service. In general, DDM equips web services with efficient methods of foreseeing how their choices of actions would impact their short-term and long-term goals, therefore opting for better decisions. We performed experiments using real data from 142 users on 4,532 web services on 64 different time slots. The experimental results, show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.

\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

@@

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
Web services \sep Community of services \sep Distributed Decision Making
\end{keyword}

@@

Over the past years, online services have become an important part of many scalable business applications. The increasing reliance on online service providers has significantly influenced the way web services are engineered. Therefore, given the dynamic and unpredictable nature of the Internet, delivering high quality services is still a critical and challenging issue. One practical solution towards delivering high quality services is utilizing intelligent decision making agents. These agents aim at maximizing their gain by exploring the best ways to provide services that satisfy end users\cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, journals/tsc/ZhengZYB13}. However, agent-based web services are functionally limited in the sense that they cannot handle a large number of requests at the same time without compromising the quality of service provided. Recent developments have attempted to shift web services from passive models, consisting of individual components, to models made up of autonomous and group-based components that share common goals. In group-based models, interaction, composition, and cooperation are the key challenges \cite{ICWS2011-1, SCC2011-1, journals/mags/BaldoniBM10, journals/jcss/CasadoYT13} that directly impact the group's overall performance in achieving common goals. To that end, we see the emergence of web service \emph{communities}, which consist of services with similar functionalities but distinct nonfunctional properties \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic, 10.1109/ARES.2008.7}. A \emph{community} of web services runs continuous performance assessment functions that regulate web services' interactions and manage their composition and cooperation.

@@

@@

\begin{table}[ht]
\caption{An example of $gain$ matrix for 3 different communities and their combinations} % title of Table
\centering % used for centering table
\scriptsize
{\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|c c c c c c} % centered columns (4 columns)
\hline\hline %inserts double horizontal lines
 & \textless348\textgreater & \textless1934\textgreater & \textless2117\textgreater & \textless348, 1934\textgreater & \textless1934, 2117\textgreater & \textless348, 1934, 2117\textgreater \\ [0.5ex] % inserts table
%heading
\hline % inserts single horizontal line
\textless348\textgreater & - & 0.282708 & 1.027081 & 0.282708 & 18.027081 & 18.027081 \\
\textless1934\textgreater & -2.637483 & - & 6.969072 & -2.637483 & 5.509583 & 4.387725 \\
\textless2117\textgreater & 5.027081 & 2.969072 & - & 5.509583 & 2.969072 & 5.509583 \\
\textless348, 1934\textgreater & 0.0 & 0.0 & -3.851432 & - & -3.851432 & -3.851432 \\
\textless1934, 2117\textgreater & 2.969072 & 0.0 & 0.0 & 2.969072 & - & 2.969072 \\
\textless348, 1934, 2117\textgreater & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & - \\ [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
}
\label{table:nonlin} % is used to refer this table in the text
\end{table}

@@

@@

\bibitem{}
